### 2013-10-02 Paper_Markdown.Rmd
Minor change in bootstrap_mat, removed `cat` calls for `j` and removed text update to improve speed.  Added a bibtex file for potential references, more text editing.

Although we cannot know the values for temperature or precipitation during this time, statistical non-analogues do exist in a modern context, and we can construct false non-analogues using a modified h-block sampling procedure

>>>>

Although we cannot know the values for temperature or precipitation during this time, statistical non-analogues do exist in a modern context, and we can construct false non-analogues using a modified h-block sampling procedure (e.g., Telford & Birks) that examines analogue distance rather than geographical distance.
